\huge Tor's Usability for Censorship Circumvention

### 2016-05-12 pets2017-paper/pets2017-paper.tex
\hyphenation{Isa-bela}
It was being broken as Is-
abela.
Left-align the env–version column of table:median_time.
To match other tables.
Add all-participant-times appendix.
Move table:median_time into a file so it can be autogenerated.
Fix grammar.

\documentclass[USenglish,oneside,twocolumn]{article}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}
%\usepackage{hyperref}

@@

@@

\begin{table}[t]
\centering
	\begin{tabular}{c r r r r}
	& First & Proxy & Bridge & Progress \\
	\noalign{\hrule}
	E1-NEW & 28\% & 0\% & 0\% & 60\% \\
	E1-OLD & 30\% & 0\% & 0\% & 29\% \\
	E2-NEW & 6\% & 5\% & 6\% & 78\% \\
	E2-OLD & 7\% & 18\% & 8\% & 45\% \\
	E3-NEW & 3\% & 5\% & 5\% & 77\% \\
	E3-OLD & 2\% & 12\% & 6\% & 64\% \\
	\end{tabular}
\caption{The median percent of time spent on each screen, which is not
necessarily the median absolute time spent on that screen. 
This percentage is computed independently for each screen; that is, a participant who spent the median percent 
of time on one screen may not be the same participant who spent the median percent
of time on other screens. Note that the time spent on the progress bar dominates the 
time spent in the interface.} 
\label{table:median_time}
\end{table}

@@

%general advice to other censorship circumvention and call for more research 
Interacting with a censorship circumvention tool users can be a complex balance of leveraging user input for local information while accounting for user trust of the software and minimizing potential risks.
When designing censorship circumvention tools, we caution against requiring first-time users to make decisions on software-specific notions (e.g. pluggable transports for Tor), answering questions that assume technical knowledge, or manually configuring components. We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software. Not only do simulated environments avoids rerouting traffic through a censoring countries' networks, its reproducibility and stability ideal for experiments.

@@

>>>>

\documentclass[USenglish,oneside,twocolumn]{article}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{adjustbox}
%\usepackage{hyperref}

@@

\hyphenation{Isa-bela}

@@

\begin{table}[t]
\centering
\input{median_time.tex}
\caption{The median percent of time spent on each screen, which is not
necessarily the median absolute time spent on that screen. 
This percentage is computed independently for each screen; that is, a participant who spent the median percent 
of time on one screen may not be the same participant who spent the median percent
of time on other screens. Note that the time spent on the progress bar dominates the 
time spent in the interface.} 
\label{table:median_time}
\end{table}

@@

%general advice to other censorship circumvention and call for more research 
Interacting with a censorship circumvention tool users can be a complex balance of leveraging user input for local information while accounting for user trust of the software and minimizing potential risks.
When designing censorship circumvention tools, we caution against requiring first-time users to make decisions on software-specific notions (e.g. pluggable transports for Tor), answering questions that assume technical knowledge, or manually configuring components. We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software. Not only do simulated environments avoid rerouting traffic through a censoring country's networks, their reproducibility and stability are ideal for experiments.

@@

\section{All Participant Times}
\label{all-participant-times}

\begin{table*}
\input{all-participant-times.tex}
\caption{
Times spent on each screen, per participant.
}
\label{table:all-participant-times}
\end{table*}
